How to Name a Real-World Object, and how not to

### 2019-12-08 papers/ACL2020/experiments.tex
deletes redundant tables

@@

\gbt{begin not integrated}
As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
\cs{Maybe the next sentences are better just in the results section, when discussing the table::} Finally, we compare against two further classifiers which are trained on the \vg labels. 
Note that all four models are optimized on the $25$K~objects in \mn. 
\gbt{end not integrated}

\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and also the explanation and doesn't add much information. I'd put the most relevant (at most two, maybe even only one) in the main paper and leave the rest for the supplementary material. TBD}

@@

\subsection{Results: Entry-Level Name Prediction}
\label{sect:exp_results}
%\paragraph{Entry-Level Name Prediction}
Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
\begin{itemize}
	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
	This shows that they do learn entry-level naming to some extent, despite being trained on VG, i.e.,~\arbitrary ground truth labels.
	\cs{I would not comment on diff. btw. the two FRCNNs, it's small compared to their diffs to the classifiers, and may be also due to the diff. implementations, and VG1600 being trained additionally on attributes.}
	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
	\item \cs{?What to keep here:} The classifiers using ResNet features are the least effective, but come close to the FRCNN object detectors on entry-level naming (columns MN, GTtrain MN), or even better  (columns VG, GTtrain VG) despite being trained on a fraction of FRCNN's training size using a simple Vanilla classifier in contrast to a fully-fledged CNN architecture.
	This confirms what we observed on the FRCNN results: and follow the pattern of learning entry-level naming  
	\item Models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than \arbitrary name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning. \cs{overfitting?}
	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
\end{itemize}

\subsection{Quantitative Analysis}
\label{sect:exp_analysis}

\paragraph{Alternative Name Prediction}
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
\end{figure}

\cs{TODO::}
Categorization of "errors" (see Figure~\ref{fig:mistakes}):
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.,\ plane vs. airplane
	\item Semantically related\\
	e.g.,\  motorcycle vs. scooter
\end{enumerate}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
		\toprule
		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		Model$_{\text{Vocab}}$	& GTtrain  
		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
		\midrule \midrule
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
		\midrule
		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf. standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake). \label{tab:exp_overview_results}}
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|rrr||rrr}
		\toprule
		& &  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
		Model$_{\text{Vocab}}$ &  GTtrain & hit &  correct &  incorrect &  hit &  correct &  incorrect \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
		FRCNN$_{\text{MN442}}$ & VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
		\midrule \midrule
		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
		\midrule 
		ResNet101$_{\text{VGMN}}$ & VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
		ResNet101$_{\text{VGMN}}$ & MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
		ResNet101$_{\text{MN442}}$ & MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
		\bottomrule

	\end{tabular}
	\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		Model$_{\text{Vocab}}$ &  GTtrain & same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
		& 	&  cluster &  & cluster & & & cluster 
		& cluster  &  & cluster & & & cluster \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
		FRCNN$_{\text{MN442}}$ & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
		\midrule \midrule
		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
		\midrule
		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
		ResNet101$_{\text{MN442}}$ & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\		
		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
		\bottomrule
	\end{tabular}

	\caption{Break-down of the results for the \textit{correct} name predictions. Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.  \textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name. \textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster). \textit{Synonym} and \textit{synonym\_cl} are analogous. \label{tab:exp_alternatives}}
\end{table*}

\paragraph{Incorrect Predictions}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
		\toprule
		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		Model$_{\text{Vocab}}$ & GTtrain  
		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\

		\midrule
		FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
		FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
		\midrule \midrule
		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
		\midrule
		ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
		ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
		ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
		ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
\end{table*}

\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600). For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name. Observations:
\begin{itemize}
	\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit. Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.  (top right matrix)
	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits. This is less the case when ResNet is finetuned on VG annotations.
	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
\end{itemize}

\begin{figure*}[t]
	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}

	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
\end{figure*}

@@

\iffalse
We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}
\fi

\iffalse
\subsection{[TBC] Predicting Entry-Level Names}
\label{sect:exp_entry}
Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?

Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.  
\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model$_{\text{Vocab}}$	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
		\midrule
		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
		FRCNN--VG2500 & VG \\
		FRCNN$_{\text{VG1600}}$ & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features$_{\text{Vocab}}$ & GTtrain  \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\ 
		FRCNN$_{\text{VG1600}}$--MN442 &  MN \\
		\midrule
		ResNet101$_{\text{VGMN}}$ & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\

>>>>

\gbt{Note: I've rewritten this intro, the previous version with the plan of what is to be covered is commented out in the tex file}

@@

\gbt{BEGIN not integrated in the text yet}
As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
\cs{Maybe the next sentences are better just in the results section, when discussing the table::} Finally, we compare against two further classifiers which are trained on the \vg labels. 
Note that all four models are optimized on the $25$K~objects in \mn. 
\gbt{END not integrated}

\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and doesn't add much information. I'd put the most relevant (at most two, maybe even only one) in the main paper and leave the rest for the supplementary material. TBD}

@@

\subsection{Results}
\label{sect:exp_results}

\gbt{To do: streamline to make consistent with motivations + expectations laid out in the previous subsection.}

Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN) \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
\begin{itemize}
	\item The FRCNN models \gbt{all models, actually} are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
	This shows that they do learn entry-level naming to some extent, despite being trained on VG, i.e.,~\arbitrary ground truth labels.
	\cs{I would not comment on diff. btw. the two FRCNNs, it's small compared to their diffs to the classifiers, and may be also due to the diff. implementations, and VG1600 being trained additionally on attributes.}
	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
	\item \cs{?What to keep here:} The classifiers using ResNet features are the least effective, but come close to the FRCNN object detectors on entry-level naming (columns MN, GTtrain MN), or even better  (columns VG, GTtrain VG) despite being trained on a fraction of FRCNN's training size using a simple Vanilla classifier in contrast to a fully-fledged CNN architecture.
	This confirms what we observed on the FRCNN results: and follow the pattern of learning entry-level naming  
	\item Models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than \arbitrary name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning. \cs{overfitting?}
	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
\end{itemize}

@@

\iffalse
We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
x	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}
\fi

\iffalse
OLD TABLE WITH MORE MEASURES

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model$_{\text{Vocab}}$	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
		\midrule
		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
		FRCNN--VG2500 & VG \\
		FRCNN$_{\text{VG1600}}$ & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features$_{\text{Vocab}}$ & GTtrain  \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\ 
		FRCNN$_{\text{VG1600}}$--MN442 &  MN \\
		\midrule
		ResNet101$_{\text{VGMN}}$ & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
